Pool Model Paper

### 2023-12-05 pool_model.tex
More citations for Bacteria modelling and ABM

- \cite{gorochowski_bsim_2012, li_nufeb_2019}: examples of another toolboxes for bacterial communities modelling (ABM).\\
More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.

@@

>>>>

- \cite{emonet_agentcell_2005, gorochowski_bsim_2012, li_nufeb_2019, kreft_bacsim_1998}: examples of another toolboxes for bacterial communities modelling (ABM).\\
More about the modelling of the motile bacteria can be seen in works:~\cite{decoene_microscopic_2011, rosser_modelling_2014, sokolov_physical_2012, li_amplified_2008}.

@@

For simulation results:
    \item \cite{farrell_mechanically_2013}: Showed the influence of mechanic interactions between bacteria in 2D system with bacteria consuming the nutritient.
    The growth of bacterial colonies where nonmotile microorganisms replicate and push each other away as they grow.
    Found a transition between two different growth regimes, controlled by the balance between growth and uptake of nutrient:\\
    Exponential growth where diffusion of the nutritient does not play any role. Sublinear growth where growth is limited by nutritient diffusion.
    (Structurally in 2D it's regimes: smooth propagating of bacterial front vs. branching.)
    \item \cite{nagarajan_agent-based_2022-1}: review on the ABM for bacterial population.
    The ABM represent a microbial colony as a group of discrete agents that are governed by a set of rules, where each agent can be an individual cell or a collection of cells.
    Can use citation when talk about general processes we are accounting as growth, uptake of nutritient, production of inhibitor, e.g.,:
    Physical interactions between agents are calculated using excluded volume interactions.
    Chemical interactions as releasing inhibitors are described using concentrations and solved using PDEs.
